SDR enhancement by clouds

### 2024-04-07 article/article.Rmd
Commit 2024-04-07 21:13

<!-- Libradtran options -->
For completeness, we will describe here the main points of the radiation simulation
procedure. We used as input the spectrum of @Kurucz1994 in the range $280$ to
$2500\,\text{nm}$, with the Libradtran radiation transfer solver "disort" on a
"pseudospherical" geometry and the "LOWTRAN" gas parameterization. For each
combination of conditions we use a SZA step of $0.2^\circ$.
<!-- Atmospheric options -->
For the atmospheric characteristics, we iterated for combinations of AOD at
$500\,\text{nm}$ ($\tau_{500\text{nm}}$) with additional offsets of $\pm1$ and
$\pm2\sigma$, and water column ($w_h$), also with offsets of $\pm1$ and $\pm2\sigma$.
We applied them on two atmospheric profiles, from the Air Force Geophysics
Laboratory (AFGL). The "AFGL atmospheric constituent profile, midlatitude summer"
(afglms) and the "AFGL atmospheric constituent profile, midlatitude winter" (afglmw)
[@Anderson1986].

<!-- Lookup table -->
To create a look-up table that aligns with our dataset, we applied some adjustments.
To account for the Sun's variability in our one-minute GHI measurements,

we corrected each modeled value 
the model's input spectrum integral, to the one of the total solar irradiance (TSI)
provided by NOAA [@Coddington2005].

Also, we applied the effect of the Earth -- Sun
distance on the irradiance, by using the distance calculated by the Astropy
[@AstropyCollaboration2022] software library. As needed, we interpolate the resulting
irradiances to the exact SZA of our measurements.  For each period of the year, we
used the appropriate atmospheric profile (afglms or afglmw).  Finally, we calculated
the clear sky irradiance value at the horizontal plane.  Thus, we were able to
emulate different atmospheric condition and levels of atmospheric clearness for the
climatological conditions of the site.  With this method, the modeled clear sky
irradiances can be directly compared to each measured one-minute value of GHI, for
different conditions of atmospheric clearness.

@@

After evaluating the modeled clear radiation for the different atmospheric
conditions, in relation to the measured GHI data, we choose as a representative of
the clear sky radiation, the case where
$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
($\text{GHI}_\text{CSm}$).
These values represent a typical atmosphere in Thessaloniki with low load of aerosols
and humidity, which are the main factor that attenuate the GHI, excluding clouds.  To
create the limit of CE identification, we created a two branched threshold, as a
function of SZA. A constant factor for low SZAs, and a higher ramped factor for
higher SZAs (Equation\nobreakspace\ref{eq:CE4}).
This is the criterion of our CE identification.
<!--
\begin{equation}
\text{CE}_\text{Threshold} = \begin{cases}
`r C4_cs_ref_ratio`, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4a}
\end{equation}
where: $\theta$ solar zenith angle.
-->
<!--
\begin{equation}
\text{CE} : \begin{cases}
 \text{GHI}_\text{i} > `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\text{GHI}_\text{i} > \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4b}
\end{equation}
where: $\theta$ is the solar zenith angle, $\text{GHI}_\text{i}$ the measured
irradiance, and $\text{GHI}_\text{mCSi}$ the selected modeled clear sky irradiance.
-->
\begin{equation}
\text{CE} : \text{GHI}_\text{i} > \text{GHI}_\text{CSlim,i}, \text{where} \begin{cases}
 \text{GHI}_\text{CSlim,i} = `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{CSm,i}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\text{GHI}_\text{CSlim,i} = \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{CSm,i}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4}
\end{equation}
where: $\theta$ is the solar zenith angle, $\text{GHI}_\text{i}$ the measured
irradiance, and $\text{GHI}_\text{CSm}$ the selected modeled clear sky irradiance, and $i$ each of the one-minute observation.

@@

- Include Example of days plot in the Appendix?
... this is clearer to understand and describe ....

>>>>

<!-- Libradtran options -->
For completeness, we will describe here the main points of the radiation simulation
procedure. We used as input the spectrum of @Kurucz1994 in the range $280$ to
$2500\,\text{nm}$, with the Libradtran radiation transfer solver "disort" on a
"pseudospherical" geometry and the "LOWTRAN" gas parameterization. For each
combination of conditions we use a SZA step of $0.2^\circ$.
<!-- Atmospheric options -->
For the atmospheric characteristics, we iterated for combinations of AOD at
$500\,\text{nm}$ ($\tau_{500\text{nm}}$) with additional offsets of $\pm1$ and
$\pm2\sigma$, and water column ($wc$), also with offsets of $\pm1$ and $\pm2\sigma$.
We applied them on two atmospheric profiles, from the Air Force Geophysics
Laboratory (AFGL). The "AFGL atmospheric constituent profile, midlatitude summer"
(afglms) and the "AFGL atmospheric constituent profile, midlatitude winter" (afglmw)
[@Anderson1986].

<!-- Lookup table -->
To create a look-up table that aligns with our dataset, we applied some adjustments.
To account for the Sun's variability, in our one-minute GHI measurements, 
we adapted each modeled value by scaling the  
model's input spectrum integral, to the corresponding total solar irradiance (TSI)
provided by NOAA [@Coddington2005].  
Also, we applied the effect of the Earth -- Sun
distance on the irradiance, by using the distance calculated by the Astropy
[@AstropyCollaboration2022] software library. As needed, we interpolate the resulting
irradiances to the exact SZA of our measurements.  For each period of the year, we
used the appropriate atmospheric profile (afglms or afglmw).  Finally, we calculated
the clear sky irradiance value at the horizontal plane.  Thus, we were able to
emulate different atmospheric condition and levels of atmospheric clearness for the
climatological conditions of the site.  With this method, the modeled clear sky
irradiances can be directly compared to each measured one-minute value of GHI, for
different conditions of atmospheric clearness.

@@

After evaluating the modeled clear radiation for the different atmospheric
conditions, in relation to the measured GHI data, we choose as a representative of
the clear sky radiation, the case where
$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
($\text{GHI}_\text{CSm}$).
These values represent a typical atmosphere in Thessaloniki with low load of aerosols
and humidity, which are the main factor that attenuate the GHI, excluding clouds.  To
create the limit of CE identification, we created a two branched threshold, as a
function of SZA. A constant factor for low SZAs, and a higher ramped factor for
higher SZAs (Equation\nobreakspace\ref{eq:CE4}).
This is the criterion of our CE identification.
<!--
\begin{equation}
\text{CE}_\text{Threshold} = \begin{cases}
`r C4_cs_ref_ratio`, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4a}
\end{equation}
where: $\theta$ solar zenith angle.
-->
<!--
\begin{equation}
\text{CE} : \begin{cases}
 \text{GHI}_\text{i} > `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\text{GHI}_\text{i} > \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4b}
\end{equation}
where: $\theta$ is the solar zenith angle, $\text{GHI}_\text{i}$ the measured
irradiance, and $\text{GHI}_\text{mCSi}$ the selected modeled clear sky irradiance.
-->
\begin{equation}
\text{CE} : \text{E}_\text{i} > \text{E}_\text{CSlim,i}, \text{where} \begin{cases}
 \text{E}_\text{CSlim,i} = `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\text{E}_\text{CSlim,i} = \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4}
\end{equation}
where: $\theta$ is the solar zenith angle, $\text{E}$ the measured
irradiance, $\text{E}_\text{CSm}$ the selected modeled clear sky irradiance, and $i$ each of the one-minute observation.

@@

- Include Example of days plot in the Appendix!
... this is clearer to understand and describe ....
